WMEIndia

### 2022-04-09 module2/WMEIndia.Rmd
state wise mean risk graphs

@@

joineddf %>%
  select(starts_with(c("Risky", "State")))%>%
  select(!starts_with(c("Risky_IND")))%>%
 mutate(State = factor(State, levels = c("Maharashtra",  "West Bengal","UP" , "Rajasthan" , "Tamilnadu"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c(Risky_Hydro:Risky_Oil))) %>%
  select(State, riskscore) %>%
  dplyr::group_by(State)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))

%>%
  ggplot(aes(x= technology, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  coord_flip()
```

>>>>

```{r, echo=FALSE}
cenrisksummary <- joineddf %>%
  group_by(State)%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(State, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean) #%>%
  #setNames(paste0('perceivedrisk.', names(.))) %>%
  #dplyr::rename(technology= perceivedrisk.technology)

cenrisksummary
```

@@

cenrisksummary %>%
  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
  ggplot(aes(x= technology, y= mean))+
  geom_bar(stat="identity", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  ylim(0,5)+
  facet_wrap(~ State)+
  #scale_fill_manual(y, values =))+
  coord_flip()
